quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-03-30 paper-quollr.Rmd
Added initial link plots description

### Interactivity

>>>>

### Link plots

There are mainly two interactive link plots can be generated. `show_link_plots()` helps to examine the fit. The function requires several arguments: points data which contain Non-linear dimension reduction data, high-dimensional data, and high-dimensional model data, and edge data where the from and to links of the edges.

`show_error_link_plots()` helps to see investigate whether the model fits the points everywhere or fits better in some places, or simply mismatches the pattern. The function requires several arguments: points data which contain Non-linear dimension reduction data, high-dimensional data, high-dimensional model data, and model error, and edge data where the from and to links of the edges.
